---
title: "Capital 21"
author: "Berent Lunde"
output: github_document
fig.caption: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


#### Datasets from the book: "Capital in the Twenty-First Century" by Thomas Piketty.

The Capital21 package provides an easy interface for the datasets used in the book "Capital in the Twenty-First Century" by Thomas Piketty.

Authored and maintained by [Berent Å. S. Lunde](https://berentlunde.netlify.com).

Installation instructions:

```{r, eval=FALSE}
library(devtools)
install_github("Blunde1/Capital21")

# Optionally run example
runExample()

```

Examples:
--------

#### Loading chapter data into global environment

```{r, message=FALSE, results='asis', warning=FALSE}
library(Capital21)

# Load and list chapter 0 data
chapter_0_data()
ls()
rm(list=ls())

# Load and list chapter 1 data
chapter_1_data()
ls()
```


#### Reproducing figures

```{r, message=FALSE, results='asis', warning=FALSE, error=FALSE}
# Packages for data wrangeling
library(ggplot2)
library(dplyr)
library(tidyr)

# Load data from Capital21
data("capital_V_income_eu")

# Melt and plot data 
p <- capital_V_income_eu %>%
    gather(key = "variable", value = "value", -year) %>%
    ggplot + 
    aes(x = year, y = value) + 
    geom_line(aes(color = variable), size=1) +
    scale_color_manual(values = c("black","red","blue")) +
    theme_minimal()
p
```
